\documentclass[10pt, a4paper]{article}

\usepackage[left=1.4cm, top=1.4cm, right=1.4cm, bottom=1.4cm]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{multicol}

\definecolor{accent}{HTML}{333333}
\definecolor{graytext}{HTML}{666666}
\definecolor{linkblue}{HTML}{2563EB}

\hypersetup{colorlinks=true,linkcolor=linkblue,urlcolor=linkblue}

\titleformat{\section}{\large\bfseries\color{accent}\uppercase}{}{0em}{}[\vspace{-0.5em}\rule{\textwidth}{0.8pt}]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[.]
\titlespacing*{\section}{0pt}{8pt}{4pt}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[R]{\small\color{graytext}\thepage}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlist[itemize]{nosep,leftmargin=1.2em,topsep=1pt}

\newcommand{\entry}[4]{{\textbf{#1}} \hfill {\small\color{graytext}#2}\\{\small #3 \hfill #4}\vspace{2pt}}
\newcommand{\projentry}[3]{{\textbf{#1}} {\small\color{graytext}| #2} \hfill {\small #3}\\}

\begin{document}

% HEADER
\begin{center}
{\LARGE\bfseries Arthur Donskoy}\\[2pt]
{\normalsize Systems Engineer $\cdot$ Quantitative Engineer $\cdot$ 3D Engine Developer}\\[3pt]
{\small
\href{https://github.com/KorsarOfficial}{github.com/KorsarOfficial} $\cdot$
\href{https://leetcode.com/u/korsarofficial}{leetcode.com/u/korsarofficial} $\cdot$
\href{https://github.com/KorsarOfficial/cv/blob/main/cv_en.pdf}{CV} $\cdot$
Astrakhan, Russia
}
\end{center}

\vspace{-2pt}

% SKILLS
\section{Skills}

\begin{tabularx}{\textwidth}{@{}r|X@{}}
\textbf{\small Languages} & C, C++20, Go, x86 Assembly, Python, JavaScript, ABAP, C\#, MATLAB \\
\textbf{\small Graphics} & Vulkan API, OpenGL, SDL2, GLFW, Compute Shaders, FMod \\
\textbf{\small Systems} & AVX2 SIMD, lock-free SPSC, \texttt{alignas(64)} cache-line padding, acquire/release ordering \\
\textbf{\small Media} & FFmpeg (libavformat, libavcodec, libswscale), LZW compression, GIF89a binary format \\
\textbf{\small Quant} & Bayesian inference (Beta-Binomial), Kelly criterion, Monte Carlo, EMA/ROC, walk-forward \\
\textbf{\small Infra} & WebSocket, REST API, Telegram Bot API, SQLite, PostgreSQL, Docker, CMake, Git, Linux \\
\end{tabularx}

\vspace{-2pt}

% EXPERIENCE
\section{Experience}

\entry{Quantitative Developer}{Feb 2026 -- Present}{Polyalphia}{Remote}
\begin{itemize}
\item Designed algorithmic trading system in Go (20,372 LOC, 131 files, 19 development phases).
\item Implemented 5 strategies: Mean Reversion (Sharpe 0.438, WR 53\%, \$112K backtest PnL), Momentum (ROC+EMA, $\kappa$=0.25), Probability Fade (random walk arbitrage, velocity filter), Time Decay (WR 85\%+), Longshot Fade (Griffith 1949 bias).
\item Built Bayesian filter (Beta-Binomial, exp forgetting), Kelly sizing ($f_{\max}$=0.20), hysteresis regime detector.
\item Architected multi-strategy orchestrator, 2-tier risk mgmt (15\%/25\% exposure, 40\% drawdown halt), WebSocket feeds, market scanner, Telegram bot, web dashboard, SQLite audit trail.
\end{itemize}

\entry{Systems Programmer (Self-employed)}{Oct 2023 -- Present}{Independent}{Remote}
\begin{itemize}
\item Developed KorsEngine: 3D Vulkan engine in pure C (1,381 commits, 148 files, 6.4 MB). PBR rendering, compute shaders, manual memory management via Vulkan allocation model.
\item Built MP4-to-GIF converter (C++20): 4.3$\times$ speedup (12.0s$\to$2.8s). Wu quantization (3D prefix sums), 32K nearest-color AVX2 cache (118M calls eliminated), Floyd-Steinberg (zero bounds checks), custom LZW compressor (8192-slot hash table), lock-free SPSC (alignas(64)), single-decode caching ($-$56\%). Final: 12\% from theoretical optimum.
\item Created VideoCutter (C++/FFmpeg/SDL2), Korscord (C++, K-Means++ color clustering), Snake Strategy Battle (C++, A* on torus $\mathbb{Z}/40\mathbb{Z} \times \mathbb{Z}/30\mathbb{Z}$).
\end{itemize}

\entry{Software Developer (Self-employed)}{Jul 2022 -- Oct 2023}{Independent}{Remote}
\begin{itemize}
\item Built robotics control suite (Python/PyQt5) for RM001-M03 via USB/CH341: trajectory presets, device scanning, emulation mode.
\item Developed GPU-accelerated 2D physics sandbox with Taichi Lang. Unity prototypes (FPS, AR, RTS).
\end{itemize}

\vspace{-2pt}

% OPEN SOURCE
\section{Open Source Contributions}

\projentry{Yandex Perforator}{Go, cluster-wide profiler}{7 PRs}
\begin{itemize}
\item $O(n){\to}O(\text{miss})$ eBPF syscalls (2-pass LRU+map), data race fix (RLock snapshot), exponential backoff, pre-size allocations, mutex release during Parse.
\end{itemize}

\projentry{Yandex Yatool}{Python/C++, build toolkit}{5 PRs}
\begin{itemize}
\item Startup $-$38ms, CPP\_FAKEID blast radius 82.7\%$\to$35\%, template instantiation $-$118s ($-$64.9\%), critical-path scheduling $-$38.7s ($-$11.8\%), hash map pre-size $-$0.26s.
\end{itemize}

\projentry{VK KPHP}{PHP/C++, PHP-to-C++ compiler}{4 PRs}
\begin{itemize}
\item \texttt{instanceof} unused class fix, \texttt{\_\_clone} parent chain walk, composer classmap autoloading, callback error messages.
\end{itemize}

\vspace{-2pt}

% EDUCATION
\section{Education}

\entry{Applied Mathematics and Computer Science}{2025 -- 2029}{Moscow Institute of Physics and Technology (MIPT)}{Remote}
{\small Department of System Programming (ISP RAS). Bachelor's degree.}

{\small Self-study: Knuth, \textit{The Art of Computer Programming}, Volumes 1--4A.}

\vspace{-2pt}

% COMPETITIONS
\section{Competitions \& Awards}

\begin{itemize}
\item \textbf{Smolathon 2025} --- Team Lead, 19th out of 80+ teams. Designed architecture and led development of a web platform for the Regional Center for Road Traffic Organization. Delivered full prototype in 24h on-site final. Responsible for architecture decisions, task decomposition, code review, and final pitch to jury. Part of ``Svoy Kod'' International Youth IT Forum, prize pool 500K RUB.
\item \textbf{Space Cup: Mission LUNA} --- Developed a lunar base construction planner with terrain analysis, infrastructure placement under safety constraints, and resource monitoring. JavaScript frontend with WebGL visualization, Python backend for terrain data processing.
\item \textbf{LeetCode} --- 70 problems solved (22 Easy, 34 Medium, 14 Hard). Overall acceptance rate 70.7\%. Hard acceptance rate \textbf{82.4\%} (14/17 submissions accepted on first or second attempt). Focus areas: graphs, dynamic programming, trees, sliding window. Solutions mapped by pattern on \href{https://miro.com/app/board/uXjVGcc9d58=/?share_link_id=838442415695}{Miro decomposition board}.
\end{itemize}

\vspace{-2pt}

\section{Languages}

\begin{tabularx}{\textwidth}{@{}r|X@{}}
\textbf{\small Russian} & Native \\
\textbf{\small English} & Technical reading/writing --- documentation, code, commits, PR descriptions in English. \\
\end{tabularx}

\vspace{-2pt}

\section{Contact}

\begin{tabularx}{\textwidth}{@{}r|X@{}}
\textbf{\small Telegram} & @korsarofficial \\
\textbf{\small GitHub} & \href{https://github.com/KorsarOfficial}{github.com/KorsarOfficial} \\
\textbf{\small LeetCode} & \href{https://leetcode.com/u/korsarofficial}{leetcode.com/u/korsarofficial} \\
\end{tabularx}

\end{document}
